\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-06-25 coqimpl.tex
Reply Comments.

There are only three kinds of inheritance we are dealing with---extend, override, and inherit. We use first-order data to encode inheritance data inside the implementation of the plugin. The inheritance data will include the information of (1) the ``type'' of the parent family, (2) a list of operation indicating how each field of the parent will be dealt with (either inherited or overrided), (3) the operations indicating newly extended fields, and (4) the ``type'' of the children family.\YZ{what is 'inheritance data'?}\EDJreply{It is just inheritance judgement, but before meta-theory is introduced, I can only say some "first-order data that represent the information of inheritance". I emphasize first order to distinguish from functor in ML community.}\YZreply{I think this is the place where you can use an example to demonstrate these three kinds of inheritance.} The surface syntax for the three kinds of inheritance are demonstrated in \cref*{fig:plugin-example3}. The implementation of overriding, inheritance, and extension is achieved by simply manipulating the internal representation of a family correspondingly---we can swap the module in the list for overriding, retain the module in the list for inheritance and add new module into the list for extension. The compilation from a family (internal representation) to a module still acts the same.

@@

\textbf{Reasoning Requires Non-Overridable.}\YZ{At this point in this section, overriding has not been discussed yet, but it is already discussing non-overridables. Should probably discuss the extensibility first.}
This compilation strategy
has already allowed fields to be type-dependent on former fields thus fulfilling
\ref{langdesign-req1}. However, the current implementation is not satisfactory enough. There are cases where we need to expose
the concrete definition of a given field (especially when we are proving
properties about it).

@@

To resolve this, we provide family sealing mechanism to simulate sigma type---we allow the
users to specify the compiled module type of a given family,\YZ{I don't understand "specify the family/compiled module type"}\EDJreply{Sorry. I rephase it into "compiled module type of a given family".}\YZreply{Still cannot see what is going on and how it is related to the sentence that follows. An example is due.}\EDJreply{Done. Please check.}
and thus we can have a
 \textit{non-overridable} (thus locally transparent) field located in
an \textit{overridable} family. Check the "MonotonicF" in \cref{fig:plugin-example3}, we simply seal
\mintinline{Coq}{f : nat → nat} and \mintinline{Coq}{p : monotonic f}
together inside an overridable family that does not allow "f"
to be overridden in any of its derived families.
Because "f" is non-overridable inside the family, its definition is
transparent and can be used to prove "p".
However, because the enclosing family of "f" is overridable, to swap the
implementation of "f", we just override the whole ``sealed'' family, like we do in "I2.MonotonicF".

>>>>

There are only three kinds of inheritance we are dealing with---extend, override, and inherit. We use first-order data to encode inheritance data inside the implementation of the plugin. The inheritance data will include the information of (1) the ``type'' of the parent family, (2) a list of operation indicating how each field of the parent will be dealt with (either inherited or overrided), (3) the operations indicating newly extended fields, and (4) the ``type'' of the children family.\YZ{what is 'inheritance data'?}\EDJreply{It is just inheritance judgement, but before meta-theory is introduced, I can only say some "first-order data that represent the information of inheritance". I emphasize first order to distinguish from functor in ML community.}\YZreply{I think this is the place where you can use an example to demonstrate these three kinds of inheritance.} The surface syntax for the three kinds of inheritance are demonstrated in the exemplar \cref*{fig:plugin-example3}. The implementation of overriding, inheritance, and extension is achieved by simply manipulating the internal representation of a family correspondingly---we can swap the module in the list for overriding, retain the module in the list for inheritance and add new module into the list for extension. The compilation from a family (internal representation) to a module still acts the same.

@@

\textbf{Reasoning Requires Non-Overridable.}\YZ{At this point in this section, overriding has not been discussed yet, but it is already discussing non-overridables. Should probably discuss the extensibility first.}\EDJreply{Added. Please Check.}
This compilation strategy
has already allowed fields to be type-dependent on former fields thus fulfilling
\ref{langdesign-req1}. However, the current implementation is not satisfactory enough. There are cases where we need to expose
the concrete definition of a given field (especially when we are proving
properties about it).

@@

To resolve this, we provide family sealing mechanism to simulate sigma type---we allow the
users to specify the compiled module type of a given family,\YZ{I don't understand "specify the family/compiled module type"}\EDJreply{Sorry. I rephase it into "compiled module type of a given family".}\YZreply{Still cannot see what is going on and how it is related to the sentence that follows. An example is due.}\EDJreply{Done. Please check.}
and thus we can have a
 \textit{non-overridable} (thus locally transparent) field located in
an \textit{overridable} family. Check the "MonotonicF" in \cref{fig:plugin-example3}, we simply seal
\mintinline{Coq}{f : nat → nat} and \mintinline{Coq}{p : monotonic f}
together inside an overridable family that does not allow "f"
to be overridden in any of its derived families.
Because "f" is non-overridable inside the family, its definition is
transparent and can be used to prove "p".
However, because the enclosing family of "f" is overridable, to swap the
implementation of "f", we just override the whole ``sealed'' family, like we do in "I2.MonotonicF". And the compiled module type of "I2.MonotonicF" will be fixed throughout the extension---it is always these two fields "f, p".

### 2022-06-25 lang-design.tex
Reply Comments.

% we want to be able to reason pattern matching as well
However, there is still difference between data recursion and induction
reasoning, because the former one is \textit{proof-relevant}. This
difference leads to another issue: \textlabel{Req (4)}{langdesign-req4}:
\textbf{we need to reason about (the computation about) extensible
pattern matching}, just like "subst_lemma" in \cref{fig:STLC-example}.
When proving "subst_lemma", we have to know "subst" is invariant on
"tt", i.e., \mintinline{Coq}{(subst i x tt) = tt}. This kind of
information requires exposing \textit{computational rules} from the
recursors.\YZ{What goes wrong if subst is not invariant or you do not
know whether subst is invariant?}\EDJreply{Then it is unprovable because substitution lemma need to know this. You can just instantiate the whole lemma -- we want  
has_type (Γ; x ↦ A) tt T ->
has_type Γ u A ->
has_type Γ (subst i x tt) T. But this final goal requires to know the
computation of subst.}\YZreply{Seems like what's missing here is to
convince the reader why exposing the definition of subst could be a
problem for family polymorphism.}

>>>>

% we want to be able to reason pattern matching as well
However, there is still difference between data recursion and induction
reasoning, because the former one is \textit{proof-relevant}. This
difference leads to another issue: \textlabel{Req (4)}{langdesign-req4}:
\textbf{we need to reason about (the computation about) extensible
pattern matching}, just like "subst_lemma" in \cref{fig:STLC-example}.
When proving "subst_lemma", we have to know "subst" is invariant on
"tt", i.e., \mintinline{Coq}{(subst i x tt) = tt}. This kind of
information requires exposing \textit{computational rules} from the
recursors.\YZ{What goes wrong if subst is not invariant or you do not
know whether subst is invariant?}\EDJreply{Then it is unprovable because substitution lemma need to know this. You can just instantiate the whole lemma -- we want  
has_type (Γ; x ↦ A) tt T ->
has_type Γ u A ->
has_type Γ (subst i x tt) T. But this final goal requires to know the
computation of subst.}\YZreply{Seems like what's missing here is to
convince the reader why exposing the definition of subst could be a
problem for family polymorphism.}\EDJreply{Actually I don't see why I need to emphasize this "as a problem". This is just a requirement like any other requirements earlier. I don't know how to show its difficulty at this early stage.}

### 2022-06-25 syntax.tex
Reply Comments.

Of course, any fields using "Wsup" and "Wrec" directly relies on the $\bW(\sigma)$ (can be spotted from \ruleref{Ind-Term} and \ruleref{Rec-Constr}) and thus non-inheritable---in these cases, "Wsup" can be understood as concrete constructors and "Wrec" are \textit{exhaustiveness checking}. These fields together with inductive types are the one sealing responsible for hiding. After compilation of linkage type into existential type, we can easily hide the \textit{concrete} definition of the inductive type while exposing all the fields using "Wsup" and "Wrec" like an abstract interface. Apparently, future fields relies on this abstract interface will have no problem on inheritance. \YZ{Does coverage checking mean exhaustiveness checking?}\EDJreply{Yes. The one make sure every case is handled in pattern-matching. Do you want me to replace the terminology using exhaustiveness checking? }\YZreply{Yes, I think exhaustiveness is standard parlance.}
Of course, since "Wsup" and "Wrec" directly rely on the concrete inductive definition, we will have to override these fields whenever inductive type is overridden. For "Wsup" we only need to override each constructor and for "Wrec" it is just doing exhaustiveness checking inside each children family. The recursor handlers however, can be safely inherited.
\YZ{I suppose the terminology 'sealing' is a reference to ML modules? In
ML, sealing has the connotation of hiding things behind an existential
type. So using the same word may cause the reader to have false
presumptions about what is going on here.}\EDJreply{You are right. Our "Sealing" is not hiding a particular field into an existential type, but our seal is make several fields together into an "existential type". Basically it hides the concrete definition of inductive type so that future fields doesn't have to be defined upon that.}\EDJreply{I will resolve this comment once I add the throughout example and you find it clear---because I haven't changed any text}

\YZ{Can we have a more concrete example of how the judgment is useful?}\EDJreply{it is done in the example section, please check.}

>>>>

Of course, any fields using "Wsup" and "Wrec" directly relies on the $\bW(\sigma)$ (can be spotted from \ruleref{Ind-Term} and \ruleref{Rec-Constr}) and thus non-inheritable---in these cases, "Wsup" can be understood as concrete constructors and "Wrec" are \textit{exhaustiveness checking}. These fields together with inductive types are the one sealing responsible for hiding. After compilation of linkage type into existential type, we can easily hide the \textit{concrete} definition of the inductive type while exposing all the fields using "Wsup" and "Wrec" like an abstract interface. Apparently, future fields relies on this abstract interface will have no problem on inheritance. \YZ{Does coverage checking mean exhaustiveness checking?}\EDJreply{Yes. The one make sure every case is handled in pattern-matching. Do you want me to replace the terminology using exhaustiveness checking? }\YZreply{Yes, I think exhaustiveness is standard parlance.}\EDJreply{Rephrased. }
Of course, since "Wsup" and "Wrec" directly rely on the concrete inductive definition, we will have to override these fields whenever inductive type is overridden. For "Wsup" we only need to override each constructor and for "Wrec" it is just doing exhaustiveness checking inside each children family. The recursor handlers however, can be safely inherited.
\YZ{I suppose the terminology 'sealing' is a reference to ML modules? In
ML, sealing has the connotation of hiding things behind an existential
type. So using the same word may cause the reader to have false
presumptions about what is going on here.}\EDJreply{You are right. Our "Sealing" is not hiding a particular field into an existential type, but our seal is make several fields together into an "existential type". Basically it hides the concrete definition of inductive type so that future fields doesn't have to be defined upon that.}\EDJreply{I will resolve this comment once I add the throughout example and you find it clear---because I haven't changed any text}

\YZ{Can we have a more concrete example of how the judgment is useful?}\EDJreply{it is done in the metatheory example section, please check.}
